---
output:
  html_document:
    toc: true
    toc_float: true
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(cache = TRUE, warning = FALSE)
```

```{r include=FALSE}
library(tidytext)
library(tidyverse)
library(sentimentr)
library(wordcloud)
library(SnowballC)
library(RColorBrewer)
library(reshape2)
library(knitr)
library(broom)
library(pander)
library(modelr)
library(caret)
library(feather)

#inport data
genre_tidy <- read_feather("../data/genre_tidy.feather")
text_tidy <- read_feather("../data/text_tidy.feather")
text_tfidf <- read_feather("../data/text_tfidf.feather")
text_raw <- read_feather("../data/text_raw.feather")
games_lda <- read_feather("../data/games_lda.feather")
```

## Word Frequency in the reviews

### General Word

First, a text cloud for all observations is drawn to provide a general picture of the text body. Unsurprisingly, the most common word used in the corpus is game itself, followed by game characteristic words like story, challenge, characters, world, and play.

```{r Text cloud - all}
text_count <- text_tidy %>%
  count(word, sort = TRUE) %>%
  with(wordcloud(word, n, max.words = 200, colors = brewer.pal(8, "Dark2"), random.order = FALSE))
```


```{r word_frequency, warning=FALSE}
text_count <- text_tidy %>%
  count(word, sort = TRUE) %>%
  arrange(desc(n)) %>%
  head(20) %>%
  ggplot(aes(word,n))+
  geom_bar(stat = "identity")+
  ggtitle("The most frequent word in game review-top20")+
  ylab ("amount")+
  xlab ("word")+
  coord_flip()
```

### Word frequency by Tfidf

Tf-idf index is applied to measure how much information a word provides. With this method we can get rid of most general words which are not specific for game reviews, and focus on those words which carry special meanings for video games.
```{r word frequency by Tfidf, warning=FALSE}
ggplot(text_tfidf[1 : 20,], aes(word, tf_idf)) +
  geom_bar(alpha = 0.8, stat = "identity") +
  labs(title = "Highest tf-idf words in All Game Reviews",
       x = NULL, y = "tf-idf") +
  coord_flip()

```

### Sentiment Word

Then, the bar plot revealing sentiment word frequeny and text clouds of positive and negative words are drawn to provide a general sentimental picture of the text body. One thing worth mention here is that the word stemming process is also applied to the emotion dictionary, nrc, which is used as the source of text's emotional categorization in this analysis. With stemming processing, words are gathered by word family and their frequency and importance indicators like tfidf provide more precise information. Moreover, we should notice that words which are considered standing for negative sentiment in the traditional way may not be that negative in game reviews. For instance, "attack" could simply mean how the game could be played without any negative feelings.

```{r word frequency bar sentiment,  echo=FALSE, warning=FALSE}
nrc <- get_sentiments("nrc") %>%
  mutate(word = wordStem(word)) %>%
  distinct()

bing <-  get_sentiments("bing") %>%
  mutate(word = wordStem(word)) %>%
  distinct()

# Sentiment words by frequency
text_sentCount <- text_tidy %>%
  inner_join(nrc, by = "word") %>%
  group_by(sentiment) %>%
  count(word)

#get the plot about the sentiment word most frequently used in game reviews
bing_word_counts <- text_tidy %>%
  inner_join(bing, by = "word") %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts %>%
  filter(n > 1800) %>%
  mutate(n = ifelse(sentiment == "negative", -n, n)) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_bar(alpha = 0.8, stat = "identity") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
```

```{r sentiment word cloud,  echo=FALSE, warning=FALSE}
# Positive emotional words by frequency
text_sentCountPo <- text_tidy %>%
  count(word, sort = TRUE) %>%
  inner_join(nrc, by = "word") %>%
  filter(sentiment %in% c("anticipation", "joy", "surprise", "trust")) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(title.size = 1.5, max.words = 200)

# Negative emotional words by frequency
text_sentCountNe <- text_tidy %>%
  count(word, sort = TRUE) %>%
  inner_join(nrc, by = "word") %>%
  filter(sentiment %in% c("anger", "disgust", "fear", "sadness")) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0)%>%
  comparison.cloud(title.size = 1.5, max.words = 200)

```

### Sentiment Intensity

Examining sentiments expressed by the text, a bar chart is drawn according to the frequency of each type of sentiment words. The strongst sentiment expressed in the text is trust, which well illustrates one of video games nature that they require group works and emphasize character strength which is dependable and can be trusted by other players.

The emotions are divided into positive ones, like trust and joy, colored in red, and negative ones, like fear and anger, colored in blue. An interesting fact is the well-balanceed positive and negative sentiments expressed in game reviews. Quite opposite to common expectation in games that they provide joy and make people happy, games, indeed, also produce negative emotions. Not only positive and negative words used are similar in number, but also they alternate in the sentiment intensity ranking as shown in the graph.
```{r Sentiment Intensity,  echo=FALSE, warning=FALSE}
text_sent <- text_tidy %>%
  inner_join(nrc, by = "word") %>%
  filter(sentiment != "positive", sentiment != "negative")

reorder_bysize <- function(x) {
  factor(x, levels = names(sort(table(x), decreasing = TRUE)))
}

ggplot(text_sent, aes(reorder_bysize(sentiment))) +
  geom_bar(fill = rep(c("salmon", "skyblue"), 4)) +
  labs(title = "Sentiment Intensity (by sentiment word count)",
       x = "Sentment",
       y = "Sentiment word count")

```

By averaging tfidf index of each word, emotional words are ranked. As we can see in the following tables, the top words are generally with more specific meaning than the ones produced by frequency. For positive words, Words like doll, presto, and kiss replace fun and time; for negative words, alien, curs and betray replace kill and combat. 
```{r Sentiment words by tf_idf,  echo=FALSE, warning=FALSE}
text_sentTfidf1 <- text_tfidf %>%
  group_by(word) %>%
  summarize(tfidf_avg = mean(tf_idf)) %>%
  right_join(text_sentCount, by = "word")

top_n(filter(text_sentTfidf1, sentiment == "disgust"), 5, tfidf_avg) %>% 
  arrange(desc(tfidf_avg)) %>% kable()

top_n(filter(text_sentTfidf1, sentiment == "joy"), 5, tfidf_avg) %>% 
  arrange(desc(tfidf_avg)) %>% kable()
```

## Sentiment Words and General Evaluation Score

### General Description
Exploratory relationship between different emotions and general evaluation scores is examined. Let's see the general description using plots about this question first. In this process, we divide all video games into 3 kinds based on the evaluation score: those games whose scores are above 8.5 are considered as "high"; those games whose scores are below 5 are considered as "low"; the rest are considered as medium.

As we can see, there are more positive words in "high" games' reviews, which is corresponded with our expectation. 
```{r positive-negative bar,  echo=FALSE, warning=FALSE}
text_tidy_level <- text_tidy %>%
  mutate(level = ifelse(GSScore > 8.5, "high",
                    ifelse(GSScore < 5, "low", "medium"))) %>%
  filter(is.na(level) == F )

level_count <- text_tidy_level %>%
  count(level)

text_sent_nrc <- text_tidy_level %>%
  inner_join(nrc, by = "word") %>%
  count(level, sentiment)

bing <- get_sentiments("bing") %>%
  mutate(word = wordStem(word)) %>%
  distinct()

text_sent_PN <- text_tidy_level %>%
  inner_join(bing, by = "word") %>%
  count(level, sentiment)

text_sent_PN %>%
  ggplot()+
  geom_bar(mapping = aes(x = level, y =n, fill = sentiment),stat = "identity", position = "fill")+
  ggtitle("The positive-negative words proportion in game reviews")+
  ylab ("percentage")+
  xlab ("The level of game score")
```
As for more specific kinds of sentiments, we also get different patterns among different kinds of games based on the evaluation scores. For high-scored games, there are more words related with trust, anticipation, joy, and less words related with anger comared with low-scored games.
```{r sentiment-score comparison,  echo=FALSE, warning=FALSE}
text_sent_nrc_analysis <- text_sent_nrc %>%
  inner_join(level_count, by = "level") %>%
  mutate(percentage = n.x / n.y)

text_sent_nrc_analysis %>%
  filter((sentiment != "negative") & (sentiment != "positive"))%>%
  ggplot(aes(sentiment, percentage))+
  geom_bar(aes(fill = sentiment), stat = "identity")+
  facet_wrap(~ level, nrow = 2)+
  ggtitle("The different types of sentiment words proportion in game reviews")+
  coord_polar()

text_sent_nrc %>%
  filter((sentiment != "negative") & (sentiment != "positive"))%>%
  ggplot()+
  geom_bar(mapping = aes(x = level, y =n, fill = sentiment),stat = "identity", position = "fill")+
  ggtitle("The different types of sentiment words proportion in game reviews")+
  ylab ("percentage")+
  xlab ("The level of game score")
```

### Explore the relationship

Then we tried to get the basic idea about the relationship between sentiment word and evaluation scores. As expected, we can observe a positive relationship between positive emotion and games' evaluation score, as well as a negative one between negative emotion and games' evaluation score. On top of that, The smoothing line reveals somewhat curvature relationships between the variable pairs. 

```{r relationship plot-PN,  echo=FALSE, warning=FALSE}
# Calculate sentiment tf_idfscore by game, 
text_sentTfidf <- text_tfidf %>%
  left_join(text_sentCount, by = "word") %>%
  group_by(GameTitle, sentiment) %>%
  summarize(tfidfScore = sum(tf_idf)) %>%
  spread(sentiment, tfidfScore) %>%
  left_join(text_raw, by = "GameTitle") %>%
  select(-`<NA>`, -Review) %>%
  na.omit()

# Exploratory
text_sentTfidf_plt <- text_sentTfidf %>%
  gather(sentiment, tfidf, anger : trust)

ggplot(filter(text_sentTfidf_plt, sentiment %in% c("positive", "negative")),
       aes(tfidf, GSScore)) + 
  geom_jitter(height = 0.1, width = 0.1, alpha = 0.2) +
  geom_smooth() +
  facet_wrap(~ sentiment)
```
Digging deeper into it, the relationships seem less obvious when dividing positive and negative emotions into sub-categories. For negative emotions, anger and  disgust appear to be relative influential ones, however the effects still not so strong.

On the other hand, we observe a slightly stronger effects of sub-category positive emotions, such as joy and trust, on the general evaluation scores.
```{r relationship plot-more sentiments,  echo=FALSE, warning=FALSE}
ggplot(filter(text_sentTfidf_plt, sentiment %in% c("anger", "disgust", "fear", "sadness")),
       aes(tfidf, GSScore)) + 
  geom_jitter(height = 0.1, width = 0.1, alpha = 0.2) +
  geom_smooth() +
  facet_wrap(~ sentiment)

ggplot(filter(text_sentTfidf_plt, sentiment %in% c("anticipation", "joy", "surprise", "trust")),
       aes(tfidf, GSScore)) + 
  geom_jitter(height = 0.1, width = 0.1, alpha = 0.2) +
  geom_smooth() +
  facet_wrap(~ sentiment)
```

## Model Building

In this research, two different modeling methods, linear regression and general additive, would be used. In addition, both mothods are applied with 5-fold cross validation as well as training-testing sample division. Also, each method is applied twice in establishing two different models, one with positive and negative emotions as independent variables and another with sub-categories of the positive and negative emotions, such as trust and anger, as independent variables.
```{r preparing for modeling,  echo=FALSE, warning=FALSE}
text_sentTfidf <- text_sentTfidf %>%
  mutate(GSScore_cat1 = cut(GSScore,
                           c(0, (mean(text_sentTfidf$GSScore) - sd(text_sentTfidf$GSScore)), (mean(text_sentTfidf$GSScore) + sd(text_sentTfidf$GSScore)), 10),
                           labels = c("Low", "Medium", "High")),
         GSScore_cat2 = cut(GSScore,
                           c(0, mean(text_sentTfidf$GSScore), 10),
                           labels = c("Low", "High")))

# Divide training and testing groups
inTraining <- resample_partition(text_sentTfidf, c(testing = 0.3, training = 0.7))
training <- inTraining$training %>% tbl_df()
testing <- inTraining$testing %>% tbl_df()

# 5-fold cross validation, repeat 10 times
fitControl <- trainControl(
  method = "repeatedcv",
  number = 5,
  repeats = 10)
```
###Linear Model

Among linear regression models, both positive and negative emotions demonstrate statistically significance, positively and negatively, in terms of their influence on general evaluation score. On the other hand, in the sub-category model, only anticipation and anger, among eight emotions, do not show significance. Surprisingly, the R square indicator is, indeed, going down from model 1 to model 2. It indicates that including those sub-categories do not provide more information explaining the general score's variance, at least in a linear way.

Another intresting find is the positive sign for the **fear emotion**. That indicates a relationships that the more fear in the process, the better general experience performance is. This is counter-intuitive at first, but actually understandable when considering the characteristics of video games that they often utilize negative emotions, such as battle and competition, in the process as a means generating positive emotions in the end.

```{r linear model,  echo=FALSE, warning=FALSE}
# Linear regression model
lm_fit1 <- train(GSScore ~ positive + negative, data = training, method = "lm", trControl = fitControl)
lm_fit2 <- train(GSScore ~ anticipation + trust + surprise + joy + sadness + anger + fear + disgust, data = training, method = "lm", trControl = fitControl)
pander(summary(lm_fit1))
```

```{r table 2,  echo=FALSE, warning=FALSE}
pander(summary(lm_fit2))
```

Finally, the testing sample division is applied to verify the robustness of the model. It shows a similar residual standard error, at around 1.5, to the training sample set's, and thus confirms the model's stability.
```{r MSE-li,  echo=FALSE, warning=FALSE}
lm_pred <- predict(lm_fit2, testing)
pander(postResample(pred = lm_pred, obs = testing$GSScore))
```

## General additive model

Due to the curved fitting line we observed in the previous exploratory section, general additive model is adopted for non-linear relationship modeling. The result is quite similar to that of linear regression model, however, it does provide better fits to several of the sub-category emotions. In the second GAM model, all the sub-categories of the positive and negative emotions show significance.

Nevertheless, somewhat surprisingly, the GAM model presents a slightly lower R squared value and a slightly higher MSE than the linear model. For these, we wouldn't be able to say that the GAM models are superior to the linear models in this context, especially non-linears models are generally much worse at providing reasonable inference of the relationships between variables.
```{r GAM,  echo=FALSE, warning=FALSE}
# General additive model
gam_fit1 <- train(GSScore ~ positive + negative, data = training, method = 'gamLoess', trControl = fitControl)
gam_fit2 <- train(GSScore ~ anticipation + trust + surprise + joy + sadness + anger + fear + disgust, data = training, method = 'gamLoess', trControl = fitControl)
pander(summary(gam_fit1)[4])
```

```{r GAM-tb2,  echo=FALSE, warning=FALSE}
pander(summary(gam_fit2)[4])
```

```{r GAM-MSE,  echo=FALSE, warning=FALSE}
gam_pred <- predict(gam_fit2, testing)
pander(postResample(pred = gam_pred, obs = testing$GSScore))
```
